---
title: "Calculating Neighborhood Features"
author: "Seth Winfree"
date: "3/18/2021"
output: html_document
---

```{r setup, include=FALSE}
library(umap)
library(pastecs)
library(ggplot2)
library(RColorBrewer)
library(purrr)
library(cluster)
library(cowplot)
library(dplyr)
library("mstknnclust")
library(RANN)
library(Rtsne)

library(igraph)
library(FNN)

library("uwot")
library("Hmisc")
library(corrplot)

library(gtools)
library(ggraph)
library(gdata)
library(colorspace)

library(circlize)
library(viridis)

library(pheatmap)

library(reshape2)

pdf.out.directory <- "C:/Users/winfrees/OneDrive - Indiana University/Projects/KPMP/Collaborations/Injury Atlas Paper/Plots/"

setwd("C:/Users/winfrees/Desktop/NeighborhoodAnalysis_032521/NeighborhoodCSVs")


neighborhood.classes.v1 <- c("MPO", "CD68", "CD3",  "Vessels", "VB", "Glomeruli",  "PT","DTL","mTAL", "cTAL",  "DCTCNT", "CD","Altered")

neighborhood.classes <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL",    "PT","DTL","DCTCNT", "CD","Alt")

cols <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")


mypalette <- colorRampPalette(cols)(25)
mypalette_13 <- colorRampPalette(cols)(13) 

```

## Introduction

Class structure:


Class structure (v1):




Class#      	Structure/ID       	Gates                                       	ROI

0	      	Neutrophils		        "MPO" AND "+lo AQP and THP"                     NA
1	      	Macrophages		        "CD68" AND "+lo AQP and THP"                    NA
2	      	T-cells			         "CD3" AND "+lo AQP and THP"                     NA
3	      	Glomeruli	          	"All"                                    	"Gloms"
4	      	Vessel			        "FActin(hi)"                                    "Vessel" in cortex
5		     Vascular Bundle		"FActin(hi)" 					"Vessel" in medulla
6	      	cTAL		            	"THP" AND "phall lo" in cortex                  cortex when combined
7	      	mTAL		            	"THP" AND "phall lo" in medulla			medulla/split by analysis 
8	      	PT			              "AQP1" AND "phall lo" in cortex                 cortex when combined
9	   	    DTL		              	"AQP1" AND "phall lo" in medulla		medulla/split by analysis     
10       	DCT/CNT/CD		        "All"                                           "CD/DCT"  
11		    CD			              "All"						"CD" in medulla             
12		    Altered			          "All"                                           "fibrosis/disrupted"
13		    Not determined		    NA						NA




#Loading and Preprocessing Datasets

```{r, preprocessing all neighborhoods}

sample.list.062321 <- c("19-0001", "19-0002", "19-0003", "19-0004", "20-0007", "20-0008", "20-0009","20-0010", "20-0011", "20-0012", "20-0039", "20-0041", "20-0042", "20-0043", "20-0044")

diagnosis.list.062321 <- c("DKD", "DKD", "CKD", "AKI", "AKI", "AKI", "DKD","CKD", "DKD", "CKD", "DKD", "AKI", "AKI", "AKI","DKD")


neighborhood.list <- list()
neighborhood.scaled.list <- list()

data <- data.frame()
data.scaled <- data.frame()
data.combined <- data.frame()
import.scaled <- data.frame()

setwd("C:/Users/winfrees/Desktop/NeighborhoodAnalysis_032521/NeighborhoodCSVs/version4")

sample.list <- list.files(path = "C:/Users/winfrees/Desktop/NeighborhoodAnalysis_032521/NeighborhoodCSVs/version4", full.names = FALSE, recursive = FALSE)

for (i in 1:length(x = sample.list )) {
  import <- read.csv(sample.list[[i]])
  print(paste(sample.list[[i]], dim(import)))
  import["CSV"] = sample.list[[i]]
  
  neighborhood.list[[i]] <- import

import <- subset(import, subset = import$Class_0_ClassFraction < 100 & import$Class_1_ClassFraction < 100 &    import$Class_2_ClassFraction < 100 & import$Class_3_ClassFraction < 100 & import$Class_4_ClassFraction < 100 &
import$Class_5_ClassFraction < 100 & import$Class_6_ClassFraction < 100 & import$Class_7_ClassFraction < 100 &
import$Class_8_ClassFraction < 100 & import$Class_9_ClassFraction < 100 & import$Class_10_ClassFraction < 100 &
import$Class_11_ClassFraction < 100 & import$Class_12_ClassFraction < 100 & import$Class_13_ClassFraction < 100)
  
print(paste(sample.list[[i]], dim(import)))

import = import[,c(1,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33)]
import.scaled <- data.frame(import)
import.scaled <- scale(import.scaled[,c(-1,-16)], center= TRUE, scale=TRUE)



  
  data <- smartbind(data,  data.frame(import))
  data.scaled <- smartbind(data.scaled, import.scaled)
  colnames(import.scaled) <- paste("Std", colnames(import.scaled), sep = "_")
  
  data.combined.build <-cbind(data.frame(import.scaled), data.frame(import))
  data.combined <- smartbind(data.combined, data.combined.build)

}  
  
data [is.na(data)] <- 0
data.scaled [is.na(data.scaled)] <- 0
data.combined [is.na(data.combined)] <- 0

data.combined$Biopsy <- substr(data.combined$CSV, 1, 7)
data.combined$Diagnosis <- diagnosis.list.062321[match(data.combined$Biopsy, sample.list.062321)]


data.combined <- data.combined[,c(15,31,30,32,1,2,3,4,5,6,7,8,9,10,11,12,13,14,16,17,18,19,20,21,22,23,24,25,26,27,28,29)]




rm(list = c("import", "import.scaled", "data.combined.build"))

#data.neighborhoods <- data.scaled

```
#Basic stats of neighborhoods
```{r}
total.cellsneighborhood <- rowSums(data[,c(2,3,4,5,6,7,8,9,10,11,12,13,14,15)])
stat.desc(total.cellsneighborhood)

hist(total.cellsneighborhood)

```

#Louvain and tSNE mapping

```{r, clustering and dimensionality reduction}
#Calculate UMAP embedding



data.subset<- sample_n(data.combined, 50000)

data.subset <- data.subset[!duplicated(data.subset[,c(5,6,7,8,9,10,11,12,13,14,15,16,17)]),]

data.subset.embedding <- data.subset[,c(5,6,7,8,9,10,11,12,13,14,15,16,17,18)]

colnames(data.subset.embedding) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL",    "PT","DTL","DCTCNT", "CD","Alt","ND")


#test_umap <- umap(scale(data.subset.embedding[,c(-14,-15)]), n_neighbors = 100, nn_method = "annoy", n_trees = 50,
#  search_k = 5000, min_dist = 0.01, verbose = TRUE,  n_threads = 20,  n_sgd_threads = 20, fast_sgd = TRUE)
#test_umap <- data.frame(test_umap)

#data.umap.large <- data.frame(data[,-15])

#data.umap.pca <- prcomp(data.scaled.subset.embedding, scale = FALSE)

#Community assignment with louvain without undefined (ND)

data.mat <- as.matrix(data.subset.embedding[,c(-15,-16)])

info.norm = data.frame()
k= 350 
knn.norm <- get.knn(data.mat, k = k)

knn.graph <- knn.norm

knn.norm = data.frame(from = rep(1:nrow(knn.norm$nn.index), 
    k), to = as.vector(knn.norm$nn.index), weight = 1/(1 + 
    as.vector(knn.norm$nn.dist)))
nw.norm = graph_from_data_frame(knn.norm, directed = FALSE)
nw.norm = simplify(nw.norm)
lc.norm = cluster_louvain(nw.norm)



test_tsne <- Rtsne(data.subset.embedding[,c(-15,-16)],  verbose = TRUE, num_threads = 20, perplexity = 200, max_iter = 1000)



kmeans <- kmeans(data.subset.embedding[,-c(14,15)], 10, iter.max = 20, nstart = 1)

data.subset.embedding$louvain = as.factor(membership(lc.norm))

data.subset.embedding$kmeans = as.factor(kmeans$cluster)

#colnames(data.subset.embedding) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CD/DCT", "CD","Alt", "ND", "biopsy", "louvain")

colnames(data.subset.embedding) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CDDCT", "CD","Alt", "ND", "louvain", "kmeans")

colnames(data.subset) <- c("Object","Biopsy", "CSV", "Diagnosis", "Std_MPO", "Std_CD68", "Std_CD3",  "Std_Glom", "Std_Vess", "Std_VB","Std_cTAL", "Std_mTAL","Std_PT","Std_DTL","Std_CD/DCT", "Std_CD","Std_Alt", "Std_ND","MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CD/DCT", "CD","Alt", "ND")


#plot

#mypalette_10 = mypalette[c(1,2,3,4,5,6,7,8,9,10)]
#mypalette_13 = mypalette[c(1,2,3,4,5,6,7,8,9,10,11,12,13)]

pdf(paste(pdf.out.directory,"tSNE_Louvain_062521.pdf",sep = ""), width = 6, height = 5)

ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset.embedding$louvain)) + geom_point(size = 1, stroke = 0.1,alpha = 1) + theme_classic() + scale_color_manual(values = mypalette) + theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_biopsy_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$Biopsy)) + geom_point(size = 1, stroke = 0.1,alpha = 1) + theme_classic() + scale_color_manual(values = mypalette)+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_diagnosis_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$Diagnosis)) + geom_point(size = 1, stroke = 0.1,alpha = 1) + theme_classic() + scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73"))+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_MPO_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$MPO)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_CD68_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$CD68)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_CD3_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$CD3)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_Glom_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$Glom)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_Vess_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$Vess)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_VB_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$VB)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_PT_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$PT)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_DTL_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$DTL)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_mTAL_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$mTAL)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_cTAL_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$cTAL)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_DCTCNTCD_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$`CD/DCT`)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_CD_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$CD)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())
dev.off()

pdf(paste(pdf.out.directory,"tSNE_Alt_062521.pdf",sep = ""), width = 6, height = 5)
ggplot(data.frame(test_tsne$Y), aes(x = X1, y = X2, colour = data.subset$Alt)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.2) + theme_classic() + scale_color_gradient(low = "gray", high = "blue") + theme(legend.title=element_blank())
dev.off()
```





#Bar plots of celltypes by neighborhood cluster

```{r}


neighborhoods <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14)

data.named.stackedbar <- data.subset[,c(19,20,21,22,23,24,25,26,27,28,29,30,31)]
data.named.stackedbar$louvain <- data.subset.embedding$louvain

data.size <- dim(data.named.stackedbar)

colnames(data.named.stackedbar) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CDDCT", "CD","Alt", "louvain")

mat <- matrix(nrow = length(neighborhoods), ncol = data.size[2]-1)
mat [is.na(mat)] <- 0

for(i in 1:length(neighborhoods)) {
  
data.named.neighborhood <- subset(data.named.stackedbar, data.named.stackedbar$louvain == neighborhoods[[i]])

data.size <- dim(data.named.neighborhood)

#pb = txtProgressBar(min = 0, max = data.size[1], initial = 0, style = 3) 

  for(j in 1:(data.size[2]-1)) {
    for(k in 1:data.size[1]) {
      mat[i,j] <- mat[i,j] + data.named.neighborhood[k,j]

    }
  } 
 #     setTxtProgressBar(pb,i, title = paste("Progress (%):" , 100*(i/length(neighborhoods))))

for(l in 1:(data.size[2]-1)) {
  
  mat[i,l] <- mat[i,l]/data.size[1]
  
}


}
#close(pb)

 



mycolors = c( "#E69F00", "#ACA75D", "#72AFBA", "#44AFD1" ,"#22A6A2"  ,"#60BA5F","#009E73", "#C0D64B", "#609F85", "#556A6A", "#AA6123", "#D36321" ,"#CF6E64", "#CC79A7","#0072B2","#C0CD58"  )

mat <- as.data.frame(mat)
colnames(mat) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CDDCT", "CD","Alt")
neighborhoods <- as.factor(neighborhoods)
mat <- cbind(mat, neighborhoods)
mat <- melt(mat)
pdf(paste(pdf.out.directory,"Clusters_StackedBar_062521.pdf",sep = ""), width = 7, height =5)
ggplot(mat, aes(fill = variable, x = neighborhoods, y = value)) + 
  geom_bar(position="fill", stat="identity", colour = "black") + scale_fill_manual(values = mypalette_13) + theme_minimal()
dev.off()
```

#Subgate cTAL

```{r}

data.named.neighborhood.cTAL <- subset(data.subset, data.named.stackedbar$louvain == 8)

data.mat.cTAL <- as.matrix(data.named.neighborhood.cTAL[,c(5,6,7,8,9,10,11,12,13,14,15,16,17)])

info.norm.cTAL = data.frame()
k= 600 
knn.norm.cTAL <- get.knn(data.mat.cTAL, k = k)

knn.graph.cTAL <- knn.norm.cTAL

knn.norm.cTAL = data.frame(from = rep(1:nrow(knn.norm.cTAL$nn.index), 
    k), to = as.vector(knn.norm.cTAL$nn.index), weight = 1/(1 + 
    as.vector(knn.norm.cTAL$nn.dist)))
nw.norm.cTAL = graph_from_data_frame(knn.norm.cTAL, directed = FALSE)
nw.norm.cTAL = simplify(nw.norm.cTAL)
lc.norm.cTAL = cluster_louvain(nw.norm.cTAL)


data.named.neighborhood.cTAL$louvain = as.factor(membership(lc.norm.cTAL))

test_tsne.ctal <- Rtsne(data.mat.cTAL,  verbose = TRUE, num_threads = 20, perplexity = 200, max_iter = 1000)

pdf(paste(pdf.out.directory,"cTALSubgate_clusters_higha__062521.pdf",sep = ""), width = 5, height = 5)

ggplot(data.frame(test_tsne.ctal$Y), aes(x = X1, y = X2, colour = data.named.neighborhood.cTAL$louvain)) + geom_point(size = 2, stroke = 0.1,alpha = 1) + theme_classic() + scale_color_manual(values = mypalette)+ theme(legend.title=element_blank())

dev.off()

pdf(paste(pdf.out.directory,"cTALSubgate_Alt_062521.pdf",sep = ""), width = 5, height = 5)

ggplot(data.frame(test_tsne.ctal$Y), aes(x = X1, y = X2, colour = data.named.neighborhood.cTAL$Alt)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.5) + theme_classic() + scale_color_gradient(low = "gray", high = "blue")+ theme(legend.title=element_blank())

dev.off()

pdf(paste(pdf.out.directory,"cTALSubgate_cTAL_062521.pdf",sep = ""), width = 5, height = 5)

ggplot(data.frame(test_tsne.ctal$Y), aes(x = X1, y = X2, colour = data.named.neighborhood.cTAL$cTAL)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.5) + theme_classic() + scale_color_gradient(low = "gray", high = "blue") + theme(legend.title=element_blank())

dev.off()

pdf(paste(pdf.out.directory,"cTALSubgate_CD3_062521.pdf",sep = ""), width = 5, height = 5)

ggplot(data.frame(test_tsne.ctal$Y), aes(x = X1, y = X2, colour = data.named.neighborhood.cTAL$CD3)) + geom_point(size = 2, stroke = 0.1, shape = 16, alpha = 0.5) + theme_classic() + scale_color_gradient(low = "gray", high = "blue") + theme(legend.title=element_blank())

dev.off()
```
#cTAL subgate stacked bar plot

```{r}

neighborhoods.ctal <- c(1,2,3,4)

data.named.stackedbar.ctal <- data.named.neighborhood.cTAL[,c(19,20,21,22,23,24,25,26,27,28,29,30,31)]
data.named.stackedbar.ctal$louvain <- data.named.neighborhood.cTAL$louvain

colnames(data.named.stackedbar.ctal) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CDDCT", "CD","Alt", "louvain")

data.size.ctal <- dim(data.named.stackedbar.ctal)

mat.ctal <- matrix(nrow = length(neighborhoods.ctal), ncol = data.size.ctal[2]-1)
mat.ctal [is.na(mat.ctal)] <- 0



for(i in 1:length(neighborhoods.ctal)) {
  
data.named.neighborhood.ctal <- subset(data.named.stackedbar.ctal, data.named.stackedbar.ctal$louvain == neighborhoods.ctal[[i]])

data.size.ctal <- dim(data.named.neighborhood.ctal)

#pb = txtProgressBar(min = 0, max = data.size[1], initial = 0, style = 3) 

  for(j in 1:(data.size.ctal[2]-1)) {
    for(k in 1:data.size.ctal[1]) {
      mat.ctal[i,j] <- mat.ctal[i,j] + data.named.neighborhood.ctal[k,j]

    }
  } 
 #     setTxtProgressBar(pb,i, title = paste("Progress (%):" , 100*(i/length(neighborhoods))))

for(l in 1:(data.size.ctal[2]-1)) {
  
  mat.ctal[i,l] <- mat.ctal[i,l]/data.size.ctal[1]
  
}


}
#close(pb)

 





mat.ctal <- as.data.frame(mat.ctal)
colnames(mat.ctal) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CDDCT", "CD","Alt")
neighborhoods.ctal <- as.factor(neighborhoods.ctal)
mat.ctal <- cbind(mat.ctal, neighborhoods.ctal)
mat.ctal <- melt(mat.ctal)
pdf(paste(pdf.out.directory,"cTALSubgate_clusters_StackedBar_062521.pdf",sep = ""), width = 5, height = 5)
ggplot(mat.ctal, aes(fill = variable, x = neighborhoods.ctal, y = value)) + 
  geom_bar(position="fill", stat="identity", colour = "black") + scale_fill_manual(values = mypalette_13) + theme_minimal()
dev.off()
```


#Chord plots and network graphs all biospies
```{r, generating circle plots and networks maps}


data.named <- data[,c(-1, -15, -16)]
colnames(data.named) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CDDCT", "CD","Alt")

plot.names.root <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CDDCT", "CD","Alt", "All")


#data.subset.chord <- sample_n(data[,c(-1, -15, -16)], 50000)

data.subset.chord <- data[,c(-1, -15, -16)]

colnames(data.subset.chord) <- c("MPO", "CD68", "CD3",  "Glom", "Vess", "VB",   "cTAL", "mTAL","PT","DTL","CDDCT", "CD","Alt")

weight.list <- c(20000, 20000,50000,20000,20000,20000,20000,20000,20000,20000,20000,20000,20000,50000)

data.subset.chord.list <- list(14)

data.subset.chord.MPO <- subset(data.named, subset = data.named$MPO > 0)
data.subset.chord.list[[1]] <-  data.subset.chord.MPO
data.subset.chord.CD68 <- subset(data.named, subset = data.named$CD68 > 0)
data.subset.chord.list[[2]] <-  data.subset.chord.CD68
data.subset.chord.CD3 <- subset(data.named, subset = data.named$CD3 > 0)
data.subset.chord.list[[3]] <-  data.subset.chord.CD3
data.subset.chord.Glom <- subset(data.named, subset = data.named$Glom > 0)
data.subset.chord.list[[4]] <-  data.subset.chord.Glom
data.subset.chord.Vess <- subset(data.named, subset = data.named$Vess > 0)
data.subset.chord.list[[5]] <-  data.subset.chord.Vess
data.subset.chord.VB <- subset(data.named, subset = data.named$VB > 0)
data.subset.chord.list[[6]] <-  data.subset.chord.VB
data.subset.chord.cTAL <- subset(data.named, subset = data.named$cTAL > 0)
data.subset.chord.list[[7]] <-  data.subset.chord.cTAL
data.subset.chord.mTAL <- subset(data.named, subset = data.named$mTAL > 0)
data.subset.chord.list[[8]] <-  data.subset.chord.mTAL
data.subset.chord.PT <- subset(data.named, subset = data.named$PT > 0)
data.subset.chord.list[[9]] <-  data.subset.chord.PT
data.subset.chord.DTL <- subset(data.named, subset = data.named$DTL > 0)
data.subset.chord.list[[10]] <-  data.subset.chord.DTL
data.subset.chord.CDDCT <- subset(data.named, subset = data.named$CDDCT > 0)
data.subset.chord.list[[11]] <-  data.subset.chord.CDDCT
data.subset.chord.CD <- subset(data.named, subset = data.named$CD > 0)
data.subset.chord.list[[12]] <-  data.subset.chord.CD
data.subset.chord.Alt <- subset(data.named, subset = data.named$Alt > 0)
data.subset.chord.list[[13]] <-  data.subset.chord.Alt
data.subset.chord.list[[14]] <-  data.subset.chord

for(l in 1 : length(data.subset.chord.list)){




data.subset.chord.item <- data.frame(data.subset.chord.list[l])

data.subset.chord.item <- sample_n(data.subset.chord.item, 10000)

data.size <- dim(data.subset.chord.item)
 
pb = txtProgressBar(min = 0, max = data.size[1], initial = 0, style = 3) 

adj.mat <- matrix(nrow = data.size[2], ncol = data.size[2])
adj.mat [is.na(adj.mat)] <- 0

for(i in 1:data.size[1]) {
  for(j in 1:data.size[2]) {
    for(k in 1:data.size[2]) {
      adj.mat[j,k] <- adj.mat[j,k] + data.subset.chord.item[i,j] * data.subset.chord.item[i,k]
      setTxtProgressBar(pb,i, title = paste("Progress (%):" , 100*(i/data.size[1])))
    }
  }  
}

close(pb)

#

graph.adj = graph_from_adjacency_matrix(adj.mat, weighted = TRUE)
graph.adj = simplify(graph.adj, edge.attr.comb="sum")


graph.adj.undirected = as.undirected(graph.adj)
E(graph.adj.undirected)$width <- 1+E(graph.adj.undirected)$weight/10000
V(graph.adj.undirected)$label <- NA


####Chord plot

circos.clear()
circos.par(start.degree = 90, gap.degree = 4, track.margin = c(-0.1, 0.1), points.overflow.warning = FALSE)
par(mar = rep(0, 4))

# color palette


# Base plot

df = data.frame(adj.mat)
diag(df) <- 0
row.names(df) <- neighborhood.classes
colnames(df) <- neighborhood.classes

grid.col = c(MPO =mypalette_13[1], CD68 =mypalette_13[2], CD3 =mypalette_13[3],  
             Glom =mypalette_13[4], Vess =mypalette_13[5], VB =mypalette_13[6],   
             cTAL =mypalette_13[7], mTAL =mypalette_13[8], PT =mypalette_13[9],
             DTL =mypalette_13[10], DCTCNT =mypalette_13[11], CD =mypalette_13[12],
             Alt=mypalette_13[13])
pdf(paste(pdf.out.directory, paste(plot.names.root[l],"_chorddiagram_062521.pdf",sep = ""), sep = ""), width = 5, height = 9)

chordDiagram(
  x = as.matrix(df), 
  directional = 2,
  link.sort = TRUE, 
  link.largest.ontop = TRUE,
  symmetric = TRUE,
  self.link = 2,
  annotationTrack = c("grid"), 
  annotationTrackHeight = mm_h(5),
  grid.col = grid.col,
  transparency = 0.5
   )

dev.off()
coords2 <- layout_in_circle(graph.adj.undirected)

pdf(paste(pdf.out.directory, paste(plot.names.root[l],"_networks_062521.pdf",sep = ""), sep = ""), width = 5, height = 9)

plot(graph.adj.undirected,layout = as.matrix(coords2), vertex.color=mypalette_13,  edge.width=1+E(graph.adj.undirected)$weight/weight.list[[l]], vertex.label=NA)

dev.off()
}
```
#Correlation plots all biospies
```{r, correlation plots}

neighborhood.classes.trimmed <- c("MPO", "CD68", "CD3",  "Glom",  "cTAL", "mTAL","PT","Alt")

data.rename <- data[,c(2,3,4,5,8,9,10,14)]
colnames(data.rename) <- neighborhood.classes.trimmed

#data.rename <- data.rename[,-c(1,2,3)]

data.rcor = rcorr(as.matrix(data.rename))
data.cor = cor(as.matrix(data.rename))

res1 <- cor.mtest(data.rename, conf.level = .95)
colors = brewer.pal(n=10, name = "RdYlGn")

pdf(paste(pdf.out.directory,"Corr_plor_062521.pdf",sep = ""), width = 6, height = 5)

corrplot(data.cor, type = "upper", p.mat = res1$p, sig.level = 0.05, insig = "blank", diag = FALSE, col = colors, tl.pos='n')

dev.off()

corrplot.mixed(data.cor, tl.col = "black",  sig.level = 0.05, insig= "blank", p.mat = res1$p, upper.col = colors, lower.col = colors)



```

#distrubition of neighborhoods by biopsy

```{r}

biopsies <- sample.list.062321

neighborhoods.names <- c("N1", "N2", "N3",  "N4", "N5", "N6",   "N7", "N8","N9","N10","N11", "N12","N13", "N14")

data.named.neighborhood.distribution <- data.subset[,c(2,19,20,21,22,23,24,25,26,27,28,29,30,31)]
data.named.neighborhood.distribution$louvain <- data.subset.embedding$louvain

data.size <- dim(data.named.neighborhood.distribution)



mat.neighbors <- matrix(nrow = length(biopsies), ncol = length(neighborhoods.names))
mat.neighbors [is.na(mat.neighbors)] <- 0

for(i in 1:length(biopsies)) {
  
data.named.biopsy <- subset(data.named.neighborhood.distribution, data.named.neighborhood.distribution$Biopsy == biopsies[[i]])



data.size <- dim(data.named.biopsy)

#pb = txtProgressBar(min = 0, max = data.size[1], initial = 0, style = 3) 

  for(j in 1:(data.size[2])) {
    for(k in 1:(data.size[1]))
    
      if(j == as.numeric(data.named.biopsy$louvain[k])){mat.neighbors[i,j] <- mat.neighbors[i,j] + 1}
     

    
  } 
 #     setTxtProgressBar(pb,i, title = paste("Progress (%):" , 100*(i/length(neighborhoods))))

#for(l in 1:(data.size[2]-1)) {
  
#  mat.neighbors[i,l] <- mat.neighbors[i,l]/data.size[1]
  
#}


}

neighborhood.distribution <- data.frame(mat.neighbors)
colnames(neighborhood.distribution) <- neighborhoods.names
rownames(neighborhood.distribution) <- biopsies

diagnosis.colors <- as.numeric(as.factor(diagnosis.list.062321))
colSide <- brewer.pal(9, "Set1")[diagnosis.colors]

heatmap(as.matrix(neighborhood.distribution), RowSideColors = colSide, scale = "row")

```

